---
title: "Useful RStudio Keyboard Shortcuts"
date: "Last Updated `r format(Sys.Date(), '%m/%d/%Y')`"
output: 
  html_document:
    theme: "cerulean"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(stringr)
library(dplyr)
library(magrittr)

# global chunk options
opts_chunk$set(echo = FALSE)

# load in the font awesome icons
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# create the my_kable function
# creates a nice table depending on the specific operating system and keystroke group
my_kable = function(OS, grp) {
  tab %>%
    filter(group == grp & os == OS) %>%
    select(desc, keystroke, gem) %>%
    kable("html", align = "llc", escape = F, col.names = c("Description", "Keystroke", 'Gem')) %>%
    kable_styling(full_width = F, bootstrap_options = c("striped", "compressed"))
}
```

```{r table-prep}
# the raw input table
tab = read.csv("table.csv", stringsAsFactors = F, na.strings = "")
colnames(tab)[1] = "os"
tab$gem[is.na(tab$gem)] = ""

# format the necessary HTML codes
tab[tab == "star" & !is.na(tab)] = "&#9733;"
tab[tab == "down" & !is.na(tab)] = "&#8681;"
tab[tab == "up" & !is.na(tab)] = "&#8679;"
tab[tab == "right" & !is.na(tab)] = "&#8680;"
tab[tab == "left" & !is.na(tab)] = "&#8678;"

# function to insert the HTML code to indicate text should be represented as a key
insert_kbd = function(k) {
  ifelse(is.na(k), NA, paste0("<kbd>", k, "</kbd>"))
}

# insert the keys
tab$k1 %<>% insert_kbd
tab$k2 %<>% insert_kbd
tab$k3 %<>% insert_kbd
tab$k4 %<>% insert_kbd

# insert the separators
tab$keystroke = paste(tab$k1, tab$sep_12, tab$k2, sep = " ")
tab$keystroke = ifelse(!is.na(tab$k3), paste(tab$keystroke, tab$sep_23, tab$k3, sep = " "), tab$keystroke)
tab$keystroke = ifelse(!is.na(tab$k4), paste(tab$keystroke, tab$sep_34, tab$k4, sep = " "), tab$keystroke)
```

When coding along with others in RStudio, the inevitable "woah, how did you do that?!" occurs when commenting out multiple lines at once, copying multiple lines down at once, or moving lines around all without touching the mousepad.

Because the complete list is totally overwhelming, I've created this short list of shortcuts I use most often and that tend to catch people's attention (particularly the "gems" under "editing" and "navigation").

You can view the source code to build this document on [<i class="fa fa-github"></i> GitHub](https://github.com/bstaton1/useful-keystrokes){target="_blank"}.

# {.tabset .tabset-fade .tabset-pills}

## <i class="fa fa-windows"></i> {.tabset .tabset-fade .tabset-pills}

A complete list of shortcuts can be accessed within RStudio using <kbd>ALT</kbd> + <kbd>SHIFT</kbd> + <kbd>K</kbd>, or [here](https://support.rstudio.com/hc/en-us/articles/200711853-Keyboard-Shortcuts){target="_blank"}.

### Execution

`r my_kable("pc", "execution")`

### Editing

`r my_kable("pc", "editing")`

### Selection

`r my_kable("pc", "selection")`

### Navigation

`r my_kable("pc", "navigation")`

### Files

`r my_kable("pc", "files")`

### Misc

`r my_kable("pc", "misc")`

### 'rmarkdown'

`r my_kable("pc", "rmd")`

### 'devtools'

`r my_kable("pc", "devtools")`

## <i class="fa fa-apple"></i> {.tabset .tabset-fade .tabset-pills}

A complete list of shortcuts can be accessed within RStudio using <kbd>OPTION</kbd> + <kbd>SHIFT</kbd> + <kbd>K</kbd>, or [here](https://support.rstudio.com/hc/en-us/articles/200711853-Keyboard-Shortcuts){target="_blank"}.

### Execution

`r my_kable("mac", "execution")`

### Editing

`r my_kable("mac", "editing")`

### Selection

`r my_kable("mac", "selection")`

### Navigation

`r my_kable("mac", "navigation")`

### Files

`r my_kable("mac", "files")`

### Misc

`r my_kable("mac", "misc")`

### 'rmarkdown'

`r my_kable("mac", "rmd")`

### 'devtools'

`r my_kable("mac", "devtools")`

#

---

**NOTES**

*  This list is by no means comprehensive.
*  Shortcuts labeled as &#9733; under the **Gem** column are those that I personally find especially useful and are specific to my work in RStudio, beyond the basics. For example, the shortcut for "Undo" is among my most frequently used keystrokes, but it is basic in that many other programs use this same one.
*  If there is a highly useful shortcut you believe is missing from this list, please submit an [issue](https://github.com/bstaton1/useful-keystrokes/issues){target="_blank"}, and I will consider adding it. 
*  If you find an error here, please do the same.
